\thesisTitle

### 2019-10-06 proposal/paper.tex
started working on the proposal

\documentclass[12pt]{scrartcl}

\usepackage[american]{babel}

@@

\usepackage{geometry}
% \geometry{a4paper,body={5.8in,9in}}
\geometry{a4paper}

\usepackage{amsmath, amsfonts, amssymb}
\usepackage{placeins}
\usepackage{subcaption}

@@

\setlength{\parindent}{0pt}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ab hier steht der eigentliche Text:
\begin{document}
\title{Thesis Title}
\subtitle{Master Thesis Proposal \& Work Plan}
% bei Masterarbeit ggf. ändern
\author{Clemens Damke\\ \small{Matriculation Number: 7011488}\\ \small{cdamke@mail.uni-paderborn.de}}
\date{\today}
\maketitle

@@

\section{Task Objectives}\label{sec:task-objectives}

\section{Task Description}\label{sec:task-description}

\section{Time-Schedule and Subtasks}\label{sec:schedule-and-subtasks}

% % %
\begin{figure}[!ht]
	\centering
	%\includegraphics[width=.9\textwidth]{timeschedule}
	\caption{Sketch of the time schedule for the work on the thesis}\label{fig:time-schedule}
\end{figure}
% % %
\section{Initial Document Structure}\label{sec:doc-structure}
\begin{enumerate}
	\item Introduction
	\item \dots
\end{enumerate}
% % %
\newpage
\bibliography{literature}
\bibliographystyle{myalphadin}

>>>>

% chktex-file 46
\documentclass[12pt]{scrartcl}

\PassOptionsToPackage{utf8}{inputenc}
\usepackage{inputenc}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage{microtype}

@@

\usepackage{geometry}
% \geometry{a4paper,body={5.8in,9in}}
\geometry{a4paper}
\renewcommand{\baselinestretch}{1.1}
\usepackage{parskip}
\setlength{\parindent}{0pt}

\usepackage{amsmath, amsfonts, amssymb}
\usepackage{bm}
\usepackage{placeins}
\usepackage{subcaption}

@@

\usepackage{hyperref}

\usepackage[nameinlink]{cleveref}
\newcommand{\crefrangeconjunction}{--}

\usepackage[						% use biblatex for bibliography
	backend=bibtex,					% 	- use biber backend (bibtex replacement) or bibtex
	style=numeric,					% 	- use alphabetic (or numeric) bib style
	natbib=true,					% 	- allow natbib commands
	hyperref=true,					% 	- activate hyperref support
	backref=true,					% 	- activate backrefs
	isbn=false,						% 	- don't show isbn tags
	url=false,						% 	- don't show url tags
	doi=false,						% 	- don't show doi tags
	urldate=long,					% 	- display type for dates
	maxnames=3,%
	minnames=1,%
	maxbibnames=5,%
	minbibnames=3,%
	maxcitenames=2,%
	mincitenames=1%
]{biblatex}
\bibliography{literature}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\thesisTitle}{Learning to Aggregate on Structured Data}
\newcommand{\thesisSubject}{Master Thesis Proposal \& Work Plan}
\newcommand{\thesisName}{Clemens Damke}
\newcommand{\thesisMail}{cdamke@mail.uni-paderborn.de}
\newcommand{\thesisMatNr}{7011488}
\hypersetup{% setup the hyperref-package options
    pdftitle={\thesisTitle},    %   - title (PDF meta)
    pdfsubject={\thesisSubject},%   - subject (PDF meta)
    pdfauthor={\thesisName},    %   - author (PDF meta)
    plainpages=false,           %   -
    colorlinks=false,           %   - colorize links?
    pdfborder={0 0 0},          %   -
    breaklinks=true,            %   - allow line break inside links
    bookmarksnumbered=true,     %
    bookmarksopen=true          %
}

\begin{document}

\title{\thesisTitle}
\subtitle{\thesisSubject}
\author{{\thesisName}\\\small{Matriculation Number: \thesisMatNr}\\\small{\href{mailto:\thesisMail}{\thesisMail}}}
\date{\today}
\maketitle

@@

Most of the commonly used supervised machine learning techniques assume that instances are represented by $d$-dimensional feature vectors $x \in \mathcal{X} = \mathcal{X}_1 \times \cdots \times \mathcal{X}_d$ for which some target value $y \in \mathcal{Y}$ should be predicted.
In the regression setting the target domain $\mathcal{Y}$ is continuous, typically $\mathcal{Y} = \mathbb{R}$, whereas $\mathcal{Y}$ is some discrete set of classes in the classification setting.

Since not all data is well-suited for a fixed-dimensional vector representation, approaches that directly consider the structure of the input data might be more appropriate in such cases.
One such case is the class of so-called \textit{``learning to aggregate''} (LTA) problems as described by \citet{Melnikov2016}.
There the instances are represented by compositions $\bm{c}$ of constituents $c_i \in \bm{c}$, i.e.\@ variable-size multisets.
The assumption in LTA problems is that for all constituents $c_i$ a local valuation $y_i \in \mathcal{Y}$ is either given or computable.
The set of those local valuations should be indicative of the overall valuation $y \in \mathcal{Y}$ of the entire composition $\bm{c}$.
The goal of LTA is to learn a variadic aggregation function $A: \mathcal{Y}^{*} \to \mathcal{Y}$ that estimates such composite valuations, i.e.\@ $\hat{y} = A(y_1, \dots, y_n)$ for a composition with $n$ constituents.
Additionally the aggregation function $A$ should be associative and commutative to fit with the multiset-structure of compositions.

\section{Related Work}\label{sec:related-work}

\section{Goals}\label{sec:goals}

\subsection{Required Goals}\label{sec:goals:req}

\subsection{Optional Goals}\label{sec:goals:opt}

\section{Approach}\label{sec:approach}

\section{Preliminary Document Structure}\label{sec:doc-structure}

\begin{enumerate}
	\item Introduction
	\item \dots
\end{enumerate}

\section{Time-Schedule}\label{sec:schedule}

\begin{figure}[!ht]
	\centering
	%\includegraphics[width=.9\textwidth]{timeschedule}
	\caption{Sketch of the time schedule for the work on the thesis}\label{fig:schedule}
\end{figure}

% % %
\newpage
{%
\renewcommand{\bibfont}{\normalfont\small}
\setlength{\biblabelsep}{5pt}
\setlength{\bibitemsep}{0.5\baselineskip plus 0.5\baselineskip} % chktex 1
\setcounter{biburllcpenalty}{9000}
\setcounter{biburlucpenalty}{9999}
\printbibliography%
}
